Beam-Helicity and Beam-Charge Asymmetries \\ in the \red{DVCS and Bethe--Heitler processes} on \\ an Unpolarised Proton Target \underline{Paper Tag: PDVCS0607 (v2.3)} \underline{Drafting Committee: DC90 (\today)}

### 2012-01-18 background_and_systematic_dual.tex
Updated with all comments from DC meeting. Need to fix plots and order of subscripts.

\section{Background Corrections and Systematic Uncertainties for the
  2006-2007 Data}
The extracted asymmetry amplitudes are subject to systematic uncertainties that
result from a combination of background processes, 
shifts in the missing-mass distributions and various detector and binning
effects determined in the same manner as in refs.~\cite{Air08,Air09}.

@@

The predominant contribution to the systematic uncertainty arises from detector
effects. These include the acceptance of the spectrometer, smearing
effects due to detector resolution (e.g. the opening angle between the scattered lepton and produced photon trajectories that can be resolved in the calorimeter), external radiation in detector material, and the finite bin width of the $-t$, $x_{\textrm{B}}$ and $Q^{2}$ projections. In order to quantify these effects, events were generated using a Monte Carlo simulation of the spectrometer that included them. An event generator based on the GPD model described in ref.~\cite{Guz06} was
used for the simulation because it\red{s output} describes the data well and was employed in ref.~\cite{Air09}. Asymmetry amplitudes were extracted
from these simulated events using the same analysis procedure used to
extract amplitudes from experimental data. In each kinematic bin, the
systematic uncertainty was determined as the difference between the asymmetry amplitude reconstructed from the simulated data and that
calculated from the GPD model at the average $-t$, $x_{\textrm{B}}$ and
$Q^{2}$ value for that bin.

The total systematic uncertainty for the 2006-2007 data sample was
determined for each kinematic bin by adding in quadrature the
  uncertainties arising from the background correction, the
  missing-mass shifts, and the detector effects.  The 1996-2005 sample also has a
systematic uncertainty from misalignment of the spectrometer~\cite{Air09}, which has been eliminated for the 2006-2007 data sample due to improved
  surveying measurements. Therefore, because the systematic uncertainty calculation for the 2006-07 data is identical to that for the 1996-2005 data, the systematic uncertainty for 2006-07 is overestimated. This overestimate is very slight, because the systematic uncertainty contribution from potential misalignment is very small.

@@

\begin{table}
 \begin{center}
\resizebox{\textwidth}{!} {
 \begin{tabular}{|c|c|c|c|c|c|c|}
  \hline
 & $A$ $\pm$ $\delta_{stat.}$ $\pm$ $\delta_{syst.}$ & Background & Missing-Mass Shift  & Detector Effects & & Total \\
  \hline
  \hline
  $A_{\textrm{LU,I}}^{\sin\phi}$ & -0.222  $\pm$  0.023  $\pm$   0.022 & 0.002 & 0.001 & 0.022 & & 0.022 \\
  \hline
  $A_{\textrm{LU,DVCS}}^{\sin\phi}$ & 0.005  $\pm$  0.023  $\pm$  0.003 & 0.002 & 0.002 & 0.001 & & 0.003 \\
  \hline
  $A_{\textrm{LU,I}}^{\sin(2\phi)}$ & 0.005  $\pm$  0.023  $\pm$   0.003 & 0.003 & 0.001 & 0.001 & & 0.003 \\
  \hline
  \hline
  $A_{\textrm{C}}^{\cos(0\phi)}$ & -0.024 $\pm$  0.004 $\pm$  0.011 & 0.001 & 0.003 & 0.010 & & 0.011 \\
  \hline
  $A_{\textrm{C}}^{\cos\phi}$ & 0.032  $\pm$  0.006 $\pm$   0.002 & 0.002 & 0.001 & 0.001 & & 0.002 \\
  \hline
  $A_{\textrm{C}}^{\cos(2\phi)}$ & -0.004  $\pm$  0.005  $\pm$   0.014 & 0.001 & 0.000 & 0.014 & & 0.014 \\
  \hline
  $A_{\textrm{C}}^{\cos(3\phi)}$ & 0.001  $\pm$   0.005   $\pm$   0.004 & 0.000 & 0.001 & 0.003 & & 0.004 \\
  \hline
 \end{tabular}
}
  \caption{The contributions to the overall systematic 
uncertainties of the extracted asymmetry amplitudes due to the
background correction, the time-dependent shifts of the missing-mass
distributions and detector effects for the 2006-2007 data. The total
systematic uncertainties of the amplitudes, shown in the
right-most column, are the individual contributions added in quadrature.}
  \label{table_systematic_contributions_0607}
\end{center}
\end{table}

>>>>

\section{Background Corrections and Systematic Uncertainties for the
  2006-2007 Data}
The extracted asymmetry amplitudes are subject to systematic uncertainties \red{contributions} that result from a combination of background processes, shifts in the missing-mass distributions\red{,} and various detector and binning effects determined in the same manner as \red{used} in refs.~\cite{Air08,Air09} \red{in orer to maintain consistency with the results published in ref.~\cite{Air09} and therefore facilitate the combination of the two data sets}.

@@

The predominant contribution to the systematic uncertainty arises from detector
effects. These include the acceptance of the spectrometer, smearing
effects due to detector resolution (e.g. the \red{minimum} opening angle between the scattered lepton and produced photon trajectories that can be resolved in the calorimeter), external radiation in detector material, \red{potential misalignment} and the finite bin width of the $-t$, $x_{\textrm{B}}$ and $Q^{2}$ projections. In order to quantify these effects, events were generated using a Monte Carlo simulation of the spectrometer that included them. An event generator based on the GPD model described in ref.~\cite{Guz06} was used for the simulation because it\red{s output} describes the data well and was employed in ref.~\cite{Air09}. Asymmetry amplitudes were extracted from these simulated events using the same analysis procedure used to
extract amplitudes from experimental data. In each kinematic bin, the
systematic uncertainty was determined as the difference between the asymmetry amplitude reconstructed from the simulated data and that
calculated from the GPD model at the average $-t$, $x_{\textrm{B}}$ and
$Q^{2}$ value for that bin.

The total systematic uncertainty for the 2006-2007 data sample was
determined for each kinematic bin by adding in quadrature the
  uncertainties arising from the background correction, the
  missing-mass shifts, and the detector effects.  The 1996-2005 sample also has a systematic uncertainty from misalignment of the spectrometer~\cite{Air09}, which has been eliminated for the 2006-2007 data sample due to improved
  surveying measurements. \red{However}, because the systematic uncertainty calculation for the 2006-07 data \red{uses the same Monte Carlo generator and reconstruction technique as was used} for the 1996-2005 data, the systematic uncertainty for 2006-07 is overestimated\red{; t}his overestimate is very slight, because the systematic uncertainty contribution from potential misalignment \red{affecting the 1996-2005 data set} is very small.

@@

\begin{table}
 \begin{center}
\resizebox{\textwidth}{!} {
 \begin{tabular}{|c|c||c|c|c|c|c|}
  \hline
 & $A$ $\pm$ $\delta_{stat.}$& Background & Missing-Mass Shift  & Detector Effects & & Total $\delta_{syst.}$ \\
  \hline
  \hline
  $A_{\textrm{LU,I}}^{\sin\phi}$ & -0.222  $\pm$  0.023  & 0.002 & 0.001 & 0.022 & & 0.022 \\
  \hline
  $A_{\textrm{LU,DVCS}}^{\sin\phi}$ & 0.005  $\pm$  0.023  & 0.002 & 0.002 & 0.001 & & 0.003 \\
  \hline
  $A_{\textrm{LU,I}}^{\sin(2\phi)}$ & 0.005  $\pm$  0.023  & 0.003 & 0.001 & 0.001 & & 0.003 \\
  \hline
  \hline
  $A_{\textrm{C}}^{\cos(0\phi)}$ & -0.024 $\pm$  0.004 & 0.001 & 0.003 & 0.010 & & 0.011 \\
  \hline
  $A_{\textrm{C}}^{\cos\phi}$ & 0.032  $\pm$  0.006 & 0.002 & 0.001 & 0.001 & & 0.002 \\
  \hline
  $A_{\textrm{C}}^{\cos(2\phi)}$ & -0.004  $\pm$  0.005 & 0.001 & 0.000 & 0.014 & & 0.014 \\
  \hline
  $A_{\textrm{C}}^{\cos(3\phi)}$ & 0.001  $\pm$   0.005 & 0.000 & 0.001 & 0.003 & & 0.004 \\
  \hline
 \end{tabular}
}
  \caption{\red{The values of the asymmetries extracted in a single bin over the entire kinematic range with their statistical uncertainties are presented in the second column of this table. The third, fourth and fifth columns show t}he contributions to the overall systematic uncertainties of the extracted asymmetry amplitudes due to the background correction, the time-dependent shifts of the missing-mass distributions and detector effects for the 2006-2007 data. The total
systematic uncertainties of the amplitudes, shown in the right-most column, are the individual contributions added in quadrature.}
  \label{table_systematic_contributions_0607}
\end{center}
\end{table}

### 2012-01-18 experiment_and_data.tex
Updated with all comments from DC meeting. Need to fix plots and order of subscripts.

An event sample was selected requiring
that the squared missing-mass $M_{\textrm{X}}^{2}=(q+M_{P}-q')^{2}$
of the $e\,p \rightarrow\, e'\,\gamma\, \textrm{X}$ measurement
corresponded to the square of the proton mass within the limits of the
energy resolution of the H{\sc ermes} spectrometer (mainly the calorimeter). Here, $q$ is the
four-momentum of the virtual photon, $p$ is the initial four-momentum
of the target proton and $q'$ is the four-momentum of the produced
photon. The ``exclusive region'' was defined as $-$($1.5$\,GeV)$^{2} <
M_{\textrm{X}}^{2}$ $<$ (1.7\,GeV)$^{2}$, as in
ref.~\cite{Air09}. This exclusive region was shifted by up to
0.17\,GeV$^{2}$ for certain subsets of the data in order to reflect observed differences in the distributions of the electron and positron data samples~\cite{Bur10}. 
The data sample in the exclusive region contains events not only involving production of real photons in which the proton remains intact, but also
events involving the excitation of the target proton to a $\Delta^+$
resonant state (``associated production''). The recoiling proton is not detected and the calorimeter resolution does not allow separation of all of the latter events from the rest of the data sample.
No systematic uncertainty is assigned for the contribution from these
events; they are treated as part of the signal. A Monte Carlo
calculation based on the parameterisation from ref.~\cite{Bra76} is
used to estimate the fractional contribution to the event sample from resonant
production in each kinematic bin --- the uncertainty on this estimate
cannot be adequately quantified because no measurements have been made
in the H{\sc ermes} kinematic region. The results of the estimate, called the associated fractions and labelled ``Assoc. fraction'', are shown in the last row of figures~\ref{bsa_xbjrange}--\ref{bca_xbjrange2} in the results section. The method used to perform this estimation is described in detail in
ref.~\cite{Air08}.

@@

The expectation value of the experimental yield $N$ is parameterised as
\begin{equation}
 \langle N(e_{\ell},P_{\ell},\phi)\rangle =
\mathcal{L}(e_{\ell},P_{\ell})\eta(e_{\ell},\phi)\sigma_{\textrm{UU}}
(\phi)\times
[1+P_{\ell}\mathcal{A}_{\textrm{LU}}^{\textrm{DVCS}}(\phi)+e_{\ell}P_{\ell}
\mathcal{A}_{\textrm{LU}}^{\textrm{I}}(\phi)+e_{\ell}\mathcal{A}_{\textrm{C}}
(\phi)],
\end{equation}
where $P_\ell$ is the beam polarisation, $\mathcal{L}$ is the integrated luminosity, $\eta$ is the detection
efficiency and d$\sigma_{\textrm{UU}}$ denotes the
cross section for an unpolarised target summed over both beam charges and
beam helicities. The asymmetries $\mathcal{A}_{\textrm{LU}}^{\textrm{DVCS}}(\phi)$, $\mathcal{A}_{\textrm{LU}}^{\textrm{I}}(\phi)$ and
$\mathcal{A}_{\textrm{C}}(\phi)$ are expanded in
$\phi$ as
\begin{equation}
 \mathcal{A}_{\textrm{LU}}^{\textrm{DVCS}}(\phi) \simeq 
A_{\textrm{LU,DVCS}}^{\sin\phi}\sin\phi 
+ \sum^{1}_{n=0} A_{\textrm{LU,DVCS}}^{\cos(n\phi)}\cos(n\phi), 
\label{aludvcs_asym}
\end{equation}
\begin{equation}
\mathcal{A}_{\textrm{LU}}^{\textrm{I}}(\phi) \simeq \sum^{2}_{n=1}
A_{\textrm{LU,I}}^{\sin(n\phi)}\sin(n\phi) 
+ \sum^{1}_{n=0} A_{\textrm{LU,I}}^{\cos(n\phi)}\cos(n\phi), 
\label{alui_asym}
\end{equation}
\begin{equation}
\mathcal{A}_{\textrm{C}}(\phi) \simeq \sum^{3}_{n=0}
A_{\textrm{C}}^{\cos(n\phi)}\cos(n\phi) 
+ A_{\textrm{C}}^{\sin\phi}\sin\phi,
\label{ac_asym}
\end{equation}
where the approximation is due to the truncation of the infinite
Fourier series that would describe \red{exactly} the fitted distribution. Only the $\sin(n\phi)$ terms of the
$\mathcal{A}_{\textrm{LU}}$ asymmetries and the $\cos(n\phi)$ terms of the
$\mathcal{A}_{\textrm{C}}$ asymmetry are motivated by the
  physical processes under investigation. The other terms
are included both as a consistency check for any off-phase
extraneous harmonics in the data and as a test of the
normalisation of the fit. These terms are expected to be
consistent with zero and are found to be so.

@@

The leading-twist asymmetry amplitudes are $A_{\textrm{C}}^{\cos(0\phi)}$, $A_{\textrm{C}}^{\cos\phi}$ and $A_{\textrm{LU,I}}^{\sin\phi}$, which are proportional to the fourier coefficients defined in eqs.~\ref{eq:c0}---\ref{eq:c1}. Whilst all of these amplitudes receive contributions from $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$, $c_{\textrm{unp},0}^{\textrm{I}}$ is kinematically suppressed in comparison to $c_{\textrm{unp},1}^{\textrm{I}}$, so $A_{\textrm{C}}^{\cos\phi}$ and $A_{\textrm{LU,I}}^{\sin\phi}$ are expected to have the largest magnitude in H{\sc ermes} kinematic conditions.

Although strictly dependent on higher-twist quantities, the asymmetry amplitudes $A_{\textrm{LU},\textrm{I}}^{\sin(2\phi)}$ and $A^{\cos(2\phi)}_{\textrm{C}}$ can also be expressed as having a dependence on $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ using the Wandzura-Wilzcek approximation~\cite{Wan}. Neglecting antiquark-gluon-quark contributions, these higher-twist dependent amplitudes can be considered as being kinematically suppressed compared to the leading-twist amplitudes.

The $A^{\cos(3\phi)}_{\textrm{C}}$ amplitude depends on the
$c_{\textrm{unp},3}^{\textrm{I}}$ Fourier coefficient and hence the
$\mathcal{C}_{\textrm{T,unp}}^{\textrm{I}}$-function. Although the CFFs
in this function are of leading twist, they relate to gluon helicity-flip GPDs and are thus suppressed by $\alpha_{\textrm{S}}/\pi$, where $\alpha_{\textrm{S}}$ is the strong coupling constant. Table~\ref{tab_amplitudes} presents the asymmetry amplitudes extracted in this analysis and the
related Fourier coefficients, dominant $\mathcal{C}$-function, and the twist-level at which the contributing GPDs enter.
\begin{table}
\begin{center}
\resizebox{\textwidth}{!} {
\begin{tabular}{|c|c|c|c|c|}
\hline
Asymmetry Amplitude& Fourier Coefficient& Dominant CFF Dependence & Twist-Level   \\ 
\hline
\hline
$A_{\textrm{LU,I}}^{\sin\phi}$ & $s_{1,\textrm{unp}}^{\textrm{I}}$  &
$\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$
&  2 \\
\hline
$A_{\textrm{LU,I}}^{\sin(2\phi)}$ & $s_{2,\textrm{unp}}^{\textrm{I}}$ 
&
$\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$
&  3 \\
\hline
\hline
$A_{\textrm{LU,DVCS}}^{\sin\phi}$ & $s_{1, \textrm{unp}}^{\textrm{DVCS}}$ &
$\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{DVCS}}$ &  3 \\
\hline
\hline
$A_{\textrm{C}}^{\cos(0\phi)}$ & $c_{0,\textrm{unp}}^{\textrm{I}}$  &
$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 2
\\
\hline
$A_{\textrm{C}}^{\cos\phi}$ & $c_{1,\textrm{unp}}^{\textrm{I}}$  &
$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 2
\\
\hline
$A_{\textrm{C}}^{\cos(2\phi)}$ & $c_{2,\textrm{unp}}^{\textrm{I}}$ &
$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 3 \\
\hline
$A_{\textrm{C}}^{\cos(3\phi)}$ & $c_{3,\textrm{unp}}^{\textrm{I}}$ &
$\mathfrak{Re}\mathcal{C}_{\textrm{T,unp}}^{\textrm{I}}$ &  2 \\
\hline
 \end{tabular}
}
\caption{Asymmetry amplitudes that can
be extracted from the available data set, the related Fourier
coefficients, dominant $\mathcal{C}$-functions and twist-levels. {The constant K is defined in ref.~\ref{eq:K}}.}
\label{tab_amplitudes}
\end{center}
\end{table}

>>>>

An event sample was selected requiring
that the squared missing-mass $M_{\textrm{X}}^{2}=(q+M_{p}-q')^{2}$
of the $e\,p \rightarrow\, e'\,\gamma\, \textrm{X}$ measurement
corresponded to the square of the proton mass\red{, $M_{p}$,} within the limits of the
energy resolution of the H{\sc ermes} spectrometer (mainly the calorimeter). \red{Recall that} $q$ is the
four-momentum of the virtual photon, $p$ is the initial four-momentum
of the target proton and $q'$ is the four-momentum of the produced
photon. The ``exclusive region'' was defined as $-$($1.5$\,GeV)$^{2} <
M_{\textrm{X}}^{2}$ $<$ (1.7\,GeV)$^{2}$, as in
ref.~\cite{Air09}. This exclusive region was shifted by up to
0.17\,GeV$^{2}$ for certain subsets of the data in order to reflect observed differences in the distributions of the electron and positron data samples~\cite{Bur10}. 
The data sample in the exclusive region contains events not only involving \red{the} production of real photons in which the proton remains intact, but also
events involving the excitation of the target proton to a $\Delta^+$
resonant state (``associated production''). The recoiling proton is not \red{considered} and the calorimeter resolution does not allow separation of all of the latter events from the rest of the data sample.
No systematic uncertainty is assigned for the contribution from these
events; they are treated as part of the signal. A Monte Carlo
calculation based on the parameterisation from ref.~\cite{Bra76} is
used to estimate the fractional contribution to the event sample from resonant
production in each kinematic bin\red{;} the uncertainty on this estimate
cannot be adequately quantified because no measurements have been made
in the H{\sc ermes} kinematic region. The results of the estimate, called the associated fractions and labelled ``Assoc. fraction'', are shown in the last row of figures~\ref{bsa_xbjrange}--\ref{bca_xbjrange2} in the results section. The method used to perform this estimation is described in detail in
ref.~\cite{Air08}.

@@

The expectation value of the experimental yield $N$ is parameterised as
\begin{equation}
 \langle N(e_{\ell},P_{\ell},\phi)\rangle =
\mathcal{L}(e_{\ell},P_{\ell})\eta(e_{\ell},\phi)\sigma_{\textrm{UU}}
(\phi)
[1+P_{\ell}\mathcal{A}_{\textrm{LU}}^{\textrm{DVCS}}(\phi)+e_{\ell}P_{\ell}
\mathcal{A}_{\textrm{LU}}^{\textrm{I}}(\phi)+e_{\ell}\mathcal{A}_{\textrm{C}}
(\phi)],
\end{equation}
where $P_\ell$ is the beam polarisation, $\mathcal{L}$ is the integrated luminosity, $\eta$ is the detection
efficiency and d$\sigma_{\textrm{UU}}$ denotes the
cross section for an unpolarised target summed over both beam charges and
beam helicities. The asymmetries $\mathcal{A}_{\textrm{LU}}^{\textrm{DVCS}}(\phi)$, $\mathcal{A}_{\textrm{LU}}^{\textrm{I}}(\phi)$ and
$\mathcal{A}_{\textrm{C}}(\phi)$ are expanded in
$\phi$ as
\begin{equation}
 \mathcal{A}_{\textrm{LU}}^{\textrm{DVCS}}(\phi) \simeq 
A_{\textrm{LU,DVCS}}^{\sin\phi}\sin\phi 
+ \sum^{1}_{n=0} A_{\textrm{LU,DVCS}}^{\cos(n\phi)}\cos(n\phi), 
\label{aludvcs_asym}
\end{equation}
\begin{equation}
\mathcal{A}_{\textrm{LU}}^{\textrm{I}}(\phi) \simeq \sum^{2}_{n=1}
A_{\textrm{LU,I}}^{\sin(n\phi)}\sin(n\phi) 
+ \sum^{1}_{n=0} A_{\textrm{LU,I}}^{\cos(n\phi)}\cos(n\phi), 
\label{alui_asym}
\end{equation}
\begin{equation}
\mathcal{A}_{\textrm{C}}(\phi) \simeq \sum^{3}_{n=0}
A_{\textrm{C}}^{\cos(n\phi)}\cos(n\phi) 
+ A_{\textrm{C}}^{\sin\phi}\sin\phi,
\label{ac_asym}
\end{equation}
where the approximation is due to the truncation of the infinite
Fourier series that would describe \red{exactly} the fitted distribution. Only the $\sin(n\phi)$ terms of the
$\mathcal{A}_{\textrm{LU}}$ asymmetries and the $\cos(n\phi)$ terms of the
$\mathcal{A}_{\textrm{C}}$ asymmetry are motivated by the
  physical processes under investigation. The other terms
are included both as a consistency check for any off-phase
extraneous harmonics in the data and as a test of the
normalisation of the fit. These terms are expected to be
consistent with zero and are found to be so.

@@

The leading-twist asymmetry amplitudes are $A_{\textrm{C}}^{\cos(0\phi)}$, $A_{\textrm{C}}^{\cos\phi}$ and $A_{\textrm{LU,I}}^{\sin\phi}$, which are proportional to the Fourier coefficients \red{$c_{0,\textrm{unp}}^{\textrm{I}}$, $c_{1,\textrm{unp}}^{\textrm{I}}$ and $s_{1,\textrm{unp}}^{\textrm{I}}$} defined in eqs.~\ref{eq:c0}---\ref{eq:s1}. Whilst all of these amplitudes receive contributions from $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$, $c_{\textrm{unp},0}^{\textrm{I}}$ is kinematically suppressed in comparison to $c_{\textrm{unp},1}^{\textrm{I}}$, so $A_{\textrm{C}}^{\cos\phi}$ and $A_{\textrm{LU,I}}^{\sin\phi}$ are expected to have the largest magnitude in H{\sc ermes} kinematic conditions.

Although strictly dependent on higher-twist quantities, the asymmetry amplitudes $A_{\textrm{LU},\textrm{I}}^{\sin(2\phi)}$ and $A^{\cos(2\phi)}_{\textrm{C}}$ can also be expressed as having a dependence on $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ using the Wandzura-Wilzcek approximation~\cite{Wan}\red{, i.e. n}eglecting antiquark-gluon-quark contributions\red{; these amplitudes that are dependent on higher-twist objects can therefore be considered as being functionally similar, but kinematically suppressed, when compared to the amplitudes that are dependent only on leading-twist objects.}

The $A^{\cos(3\phi)}_{\textrm{C}}$ amplitude depends on the
$c_{\textrm{unp},3}^{\textrm{I}}$ Fourier coefficient and hence the
$\mathcal{C}_{\textrm{T,unp}}^{\textrm{I}}$-function. Although the CFFs
in this function are of leading twist, they relate to gluon helicity-flip GPDs and are thus suppressed by $\alpha_{\textrm{S}}/\pi$, where $\alpha_{\textrm{S}}$ is the strong coupling constant. Table~\ref{tab_amplitudes} presents the asymmetry amplitudes extracted in this analysis and\red{, for each of them,} the
related \red{dominant} Fourier coefficient \red{and} $\mathcal{C}$-function, and the twist-level at which the contributing GPDs enter.
\begin{table}
\begin{center}
\resizebox{\textwidth}{!} {
\begin{tabular}{|c|c|c|c|c|}
\hline
Asymmetry Amplitude& Fourier Coefficient& Dominant CFF Dependence & Twist-Level   \\ 
\hline
\hline
$A_{\textrm{LU,I}}^{\sin\phi}$ & $s_{1,\textrm{unp}}^{\textrm{I}}$  &
$\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$
&  2 \\
\hline
$A_{\textrm{LU,I}}^{\sin(2\phi)}$ & $s_{2,\textrm{unp}}^{\textrm{I}}$ 
&
$\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$
&  3 \\
\hline
\hline
$A_{\textrm{LU,DVCS}}^{\sin\phi}$ & $s_{1, \textrm{unp}}^{\textrm{DVCS}}$ &
$\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{DVCS}}$ &  3 \\
\hline
\hline
$A_{\textrm{C}}^{\cos(0\phi)}$ & $c_{0,\textrm{unp}}^{\textrm{I}}$  &
$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 2
\\
\hline
$A_{\textrm{C}}^{\cos\phi}$ & $c_{1,\textrm{unp}}^{\textrm{I}}$  &
$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 2
\\
\hline
$A_{\textrm{C}}^{\cos(2\phi)}$ & $c_{2,\textrm{unp}}^{\textrm{I}}$ &
$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 3 \\
\hline
$A_{\textrm{C}}^{\cos(3\phi)}$ & $c_{3,\textrm{unp}}^{\textrm{I}}$ &
$\mathfrak{Re}\mathcal{C}_{\textrm{T,unp}}^{\textrm{I}}$ &  2 \\
\hline
 \end{tabular}
}
\caption{Asymmetry amplitudes that can
be extracted from the available data set, the related Fourier
coefficients, dominant $\mathcal{C}$-functions and twist-levels. {The constant K is defined in eq..~\ref{eq:K}}.}
\label{tab_amplitudes}
\end{center}
\end{table}

### 2012-01-18 frame_dual.tex
Updated with all comments from DC meeting. Need to fix plots and order of subscripts.

\abstract{
Beam-helicity and beam-charge asymmetries in the hard exclusive leptoproduction of real photons from an unpolarised proton target by a 27.6\,GeV lepton beam 
are extracted from the H{\sc ermes} data set of 2006-2007 using a
missing-mass event selection technique. The asymmetry
amplitudes extracted from the new data set are more
precise than those extracted from the earlier data
set of 1996-2005 previously analysed in the same manner by H{\sc ermes}. Results from the two data sets are 
compatible with each other. Results from these combined data sets are
extracted and are the most precise asymmetry amplitude measurements made in the H{\sc ermes} kinematic region using a missing-mass event selection technique.
}
\keywords{lepton-nucleon scattering}

>>>>

\abstract{
Beam-helicity and beam-charge asymmetries in the hard exclusive leptoproduction of real photons from an unpolarised proton target by a 27.6\,GeV lepton beam 
are extracted from the H{\sc ermes} data set of 2006-2007 using a
missing-mass event selection technique. The asymmetry
amplitudes extracted from \red{this} data set are more
precise than those extracted from the earlier data
set of 1996-2005 previously analysed in the same manner by H{\sc ermes}. \red{The r}esults from the two data sets are 
compatible with each other. Results from these combined data sets are
extracted and \red{constitute} the most precise asymmetry amplitude measurements made in the H{\sc ermes} kinematic region using a missing-mass event selection technique.
}
\keywords{lepton-nucleon scattering}
